insert title here

### 2020-12-10 slides.Rmd
Finished playoff structure slide

# Playoff Structure
- For the previous conference/division structure,

>>>>

# Playoff Structure
- For the previous conference/division structure, the top two teams in each division secure a berth into the playoffs
- The remaining four slots are claimed by the two teams in each conference with the next highest point total regardles of the division. These are known as the wild cards.
- The process is similar with the new divisions in each conference
- Now the top three teams in each division secure a playoff berth and the wild cards are chosen using the same process as before
